---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures",
  out.width = "100%"
)
```

# Blasso： Integrating LASSO cox regression and bootstrapping algorithm to find best prognostic features


##The package is not yet on CRAN. You can install from Github:

```{r,message=FALSE}

if (!requireNamespace("devtools", quietly = TRUE)) install.packages("devtools")
if (!requireNamespace("Blasso", quietly = TRUE))  devtools::install_github("DongqiangZeng0808/Blasso")

```

##Loading packages,Main documentation is on the `best_predictor_cox` and `best_predictor_binominal` function in the package:
```{r, warning=FALSE,message=FALSE}

library(Blasso) 
help("best_predictor_cox")
help("best_predictor_binomial")

```

##Supplementary data

```{r}
data("target")
head(target)

data("features")
features[1:5,1:5]

```

##Usage-1: Cox-regression model

```{r,message=FALSE,warning=FALSE}

res<-best_predictor_cox(target_data = target, 
                        features = features, 
                        status = "status",
                        time = "time",
                        nfolds = 10,
                        permutation = 300,
                        show_progress = FALSE)
head(res$res)

```


##Usage-2: Binomial model

```{r,message=FALSE,warning=FALSE}

res<-best_predictor_binomial(target_data = target, 
                             features = features,
                             response = "status",
                             nfolds = 10,
                             permutation = 300,
                             show_progress = FALSE)
head(res$res)

```

##Session Info

```{r,message=FALSE}
sessionInfo()
```


##References
Zeng D, Ye Z, Wu J, Zhou R, Fan X, Wang G, Huang Y, Wu J, Sun H, Wang M, Bin J, Liao Y, Li N, Shi M, Liao W. Macrophage correlates with immunophenotype and predicts anti-PD-L1 response of urothelial cancer. Theranostics 2020; 10(15):7002-7014. [doi:10.7150/thno.46176](http://www.thno.org/v10p7002.html)

---------
Contact:
E-mail any questions to dongqiangzeng0808@gmail.com
